VIPRE: Virtualized Intermittently-Powered Runtime Environment

### 2017-07-09 paper/intro.tex
Paragraph 1 revised with 10 new references added

Advances in processor efficiency along with the development of energy-harvesting power systems has created a new category of devices that require neither a battery nor a tethered power supply. These devices operate entirely using energy extracted from their environment, such as RF energy~\cite{}, photovoltaics~\cite{}, and vibration~\cite{}. Incorporating compute, storage, sensing, and communication hardware, such energy-independent devices are a promising candidate as the underlying technology for emerging Internet of Things (IoT) applications, in- and on-body medical applications~\cite{}, and emerging applications, like energy-harvesting nano-satellites~\cite{}.

>>>>

Advances in processor efficiency along with the development of energy-harvesting power systems has created a new category of devices that require neither a battery nor a tethered power supply~\cite{prasad_comst_2014,lucia_snapl_2017,soyata_csm_2016}. These devices operate entirely using energy extracted from their environment, such as RF energy~\cite{rf_powered_computing_gollakota_2014}, photovoltaic components~\cite{margolies_infocom_2016,margolies_tosn_2016}, and vibration~\cite{gorlatova_sigmetrics_2014}. Incorporating compute, storage, sensing, and communication hardware, such energy-independent devices are a promising candidate as the underlying technology for emerging Internet of Things (IoT) applications~\cite{ku_cst_2016}, in-body~\cite{nadeau_naturebio_2017} and on-body~\cite{bandodkar_electroanalysis_2015} medical applications, and emerging applications, like energy-harvesting nano-satellites~\cite{kicksat}.
